### 2017-11-03 submission/manuscript.Rmd
amend abstract and discussion

loadLibs(c("tidyverse", "scales"))

@@

**Conclusions.** This data provides support for the idea of the "driver-passenger" model in both adenoma and carinoma. The data is much stronger for carcinoma and this may in part be due to the low power to detect more subtle changes in the majority of studies that have been performed to date.

@@

Our carcinoma observations fit the driver-passenger model and support this concept within the framework of the transition from adenoma to carcinoma. In contrast, with the present data we can only suggest that the adenoma observations might fit well with this model but the changes that occur at this timepoint are small and possibly focal to the adenoma or specific location. The stepwise decrease in diversity suggests that the adenoma community is not normal but this change is subtle. Although there may be localized changes that do depend on the driver-passenger model, supported by the *Porphyromonas* finding in adenoma stool and the relative total abundance of all four CRC associated genera in tissue, there may be another process involved that ultimately exacerbates the condition from a subtle localized change to a global community one. It is possible to hypothesize that at early stages of the diease, how the host interacts to these subtle changes could be the catlyst that ultimately leads to this larger global dysfunctional community.

@@

>>>>

loadLibs(c("tidyverse", "scales", "knitr", "rmarkdown"))

@@

**Conclusions.** This data provides support for the idea of the "driver-passenger" model in carinoma but only partially for adenoma. The data is much stronger for carcinoma and this may in part be due to the low power to detect more subtle changes in the majority of studies that have been performed to date.

@@

Our carcinoma observations fit the driver-passenger model and support this concept within the framework of the transition from adenoma to carcinoma. In contrast, with the present data we can only suggest that the adenoma observations might fit with this model but the changes that occur at this timepoint are small and possibly focal to the adenoma or specific location. The stepwise decrease in diversity suggests that the adenoma community is not normal but this change is subtle. Although there may be localized changes that do depend on the driver-passenger model, supported by the *Porphyromonas* finding in adenoma stool and the relative total abundance of all four CRC associated genera in tissue [Figure 3], there may be another process involved that ultimately exacerbates the condition from a subtle localized change to a global community one. The poor performance of the Random Forest models for classifying adenoma based only on the microbiota would suggest that this is the case. It is possible to hypothesize that at early stages of the diease, how the host interacts to these subtle changes could be the catlyst that ultimately leads to this larger global dysfunctional community.

@@

studies <- c("Ahn", "Baxter", "Brim", "Burns", "Chen", "Dejea", "Flemer", "Geng", "Hale", "Lu", "Sanapareddy", "Wang", "Weir", "Zeller")

kable(table1, format = "markdown", align = 'c', padding = 2)
```

### 2017-11-03 submission/manuscript.tex
amend abstract and discussion

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\textbf{Conclusions.} This data provides support for the idea of the
``driver-passenger'' model in both adenoma and carinoma. The data is
much stronger for carcinoma and this may in part be due to the low power
to detect more subtle changes in the majority of studies that have been
performed to date.

@@

Our carcinoma observations fit the driver-passenger model and support
this concept within the framework of the transition from adenoma to
carcinoma. In contrast, with the present data we can only suggest that
the adenoma observations might fit well with this model but the changes
that occur at this timepoint are small and possibly focal to the adenoma
or specific location. The stepwise decrease in diversity suggests that
the adenoma community is not normal but this change is subtle. Although
there may be localized changes that do depend on the driver-passenger
model, supported by the \emph{Porphyromonas} finding in adenoma stool
and the relative total abundance of all four CRC associated genera in
tissue, there may be another process involved that ultimately
exacerbates the condition from a subtle localized change to a global
community one. It is possible to hypothesize that at early stages of the
diease, how the host interacts to these subtle changes could be the
catlyst that ultimately leads to this larger global dysfunctional
community.

@@

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\textbf{Conclusions.} This data provides support for the idea of the
``driver-passenger'' model in carinoma but only partially for adenoma.
The data is much stronger for carcinoma and this may in part be due to
the low power to detect more subtle changes in the majority of studies
that have been performed to date.

@@

Our carcinoma observations fit the driver-passenger model and support
this concept within the framework of the transition from adenoma to
carcinoma. In contrast, with the present data we can only suggest that
the adenoma observations might fit with this model but the changes that
occur at this timepoint are small and possibly focal to the adenoma or
specific location. The stepwise decrease in diversity suggests that the
adenoma community is not normal but this change is subtle. Although
there may be localized changes that do depend on the driver-passenger
model, supported by the \emph{Porphyromonas} finding in adenoma stool
and the relative total abundance of all four CRC associated genera in
tissue {[}Figure 3{]}, there may be another process involved that
ultimately exacerbates the condition from a subtle localized change to a
global community one. The poor performance of the Random Forest models
for classifying adenoma based only on the microbiota would suggest that
this is the case. It is possible to hypothesize that at early stages of
the diease, how the host interacts to these subtle changes could be the
catlyst that ultimately leads to this larger global dysfunctional
community.

@@

\begin{longtable}[]{@{}cccc@{}}
\toprule
country & year & cases & population\tabularnewline
\midrule
\endhead
Afghanistan & 1999 & 745 & 19987071\tabularnewline
Afghanistan & 2000 & 2666 & 20595360\tabularnewline
Brazil & 1999 & 37737 & 172006362\tabularnewline
Brazil & 2000 & 80488 & 174504898\tabularnewline
China & 1999 & 212258 & 1272915272\tabularnewline
China & 2000 & 213766 & 1280428583\tabularnewline
\bottomrule
\end{longtable}
